<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2014-09-03 ants2015build.Rmd
WIP: regular update

---
title: <span style="color:red;">How to build a house with<br />Advanced Normalization Tools (*ANTs*)</span>
author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
bibliography: REFERENCES.bib
logo:    logo.jpg
output:
  pdf_document:
    toc: true
    highlight: zenburn
  beamer_presentation:
    toc: true
    fig_width: 7
    fig_height: 6
  html_document:
    toc: true
    theme: readable
  revealjs_presentation:
    pandoc_args: [ "--slide-level", "2" ]
    incremental: true
    widescreen: true
    smaller: false
    theme: night
    transition: fade
    highlight: zenburn
    center: true
    self_contained: false
  ioslides_presentation:
    css: atk.css
    incremental: false
    widescreen: true
    smaller: false
    fig_width: 5
---

@@

@@

```
    An algorithm must use prior knowledge about a problem 
    to do well on that problem

>>>>

---
title: <span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>
author: Brian B. Avants (<span style="color:blue;">PENN</span>) and <br />Nicholas J. Tustison (<span style="color:orange;">UVA</span>)
bibliography: REFERENCES.bib
logo:    logo.jpg
output:
  pdf_document:
    toc: true
    highlight: zenburn
  beamer_presentation:
    toc: true
    fig_width: 7
    fig_height: 6
  html_document:
    toc: true
    theme: readable
  revealjs_presentation:
    pandoc_args: [ "--slide-level", "2" ]
    incremental: true
    widescreen: true
    smaller: false
    theme: night
    transition: fade
    highlight: zenburn
    center: true
    self_contained: false
  ioslides_presentation:
    css: atk.css
    incremental: false
    widescreen: true
    smaller: false
    fig_width: 5
---

@@

... just do a better registration (tell story) ...

@@

```
    An algorithm must use prior knowledge about a problem 
    to do well on that problem 
```
